Summarize twas: chr17 to 22

### 2020-09-25 analysis/simulation-multi-ukbchr17to22-gtex.adipose_susieprior.Rmd
susie I multi

* The prior used is: 
```{r  par1-t}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
susiedir <- "/home/simingz/causalTWAS/simulations/simulation_susietest_20200721/20200721-1-fixprior_rpip0.5/"
```
* susie results: 
```{r cali 1-t, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior2.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3)); cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP"); cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP"); cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

@@

# Simulation 1-x, setting 1

>>>>

* The prior used is: 
```{r  par1-t}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
susiedir <- "/home/simingz/causalTWAS/simulations/simulation_susietest_20200721/20200721-1-fixprior_rpip0.5/"
```
* susie results: 
```{r cali 1-t, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior2.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3))
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

## Regions rPIP > 0.9, simulation 3-x
We run 50 simulations and run susie using the true parameter (gene and snp pi1) as prior. We run susie for regions with regional sum of pip from mr.ash2s for both genes and snps > 0.9. run susie with L= 2.

* The true parameters we used to simulate data: 
```{r  true par-t0.9}
susiedir <- "/home/simingz/causalTWAS/simulations/simulation_susietest_20200721/20200721-3-fixprior_rpip0.9/"
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_2.txt"), header = T)
t(par[,2, drop = F])
```

* The prior used is: 
```{r  par1-t0.9}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1-t0.9, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3))
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

## All regions, simulation 3-x
We run susie for all regions. Run susie with L=1.

* The true parameters we used to simulate data: 
```{r  true par-a3}
susiedir <- "/project2/mstephens/causalTWAS/simulations/simulation_susietest_20200721/20200721-3-fixprior_allregions/"
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_2.txt"), header = T)
t(par[,2, drop = F])
```

* The prior used is: 
```{r  par1-a3}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1-a3, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior2.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3)); 
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

## Test susieI results
# Simulation 1-x, setting 1
